Future Evolution of CSMA Protocols for the IEEE 802.11 Standard

### 2013-03-06 paper.tex
made differences

\Az{We have evaluated the protocols under discussion in a very simple scenario using ideal channel, ideal clocks, and in saturation conditions. Furthermore, all the participating stations use the same protocol and have a single traffic  class. Our proposed protocol is based on CSMA/ECA, which is shown \cite{?} to work well in non-ideal conditions, and, although not presented in this manuscript, simulation results confirm that CSMA/ECA with hysteresis and fair-share inherits the flexibility and robustness of its predecessors.

@@

The authors would like to thank the anonymous reviewers for their corrections, helpful comments and suggestions for future work. The authors are also thankful to Alessandro Checco for helping in the preparation of the related work section.

>>>>

\Az{We have evaluated the protocols under discussion in a very simple scenario using ideal channel, ideal clocks, and in saturation conditions. Furthermore, all the participating stations use the same protocol and have a single traffic  class. Our proposed protocol is based on CSMA/ECA, which is shown \cite{he2009srb,barcelo2010fcc} to work well in non-ideal conditions, and, although not presented in this manuscript, simulation results confirm that CSMA/ECA with hysteresis and fair-share inherits the flexibility and robustness of its predecessors.

@@

The authors would like to thank the anonymous reviewers for their corrections, helpful comments and suggestions for future work.
